---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Color Palettes from Node's Colormap module.

This is an R package that allows you to generate colors from color palettes defined in Node [colormap](https://github.com/bpostlethwaite/colormap) module.

## Installation

Requires [V8](https://cran.r-project.org/web/packages/V8/index.html)

```{r install, eval=FALSE}
if(!require("V8")) install.packages("V8")
if(!require("devtools")) install.packages("devtools")
devtools::install_github("bhaskarvk/colormap")
```

## Usage

There is only one function `colormap` which takes 4 optional arguments

- colormap: A string representing one of the 44 built-in colormaps.\n You can use the `colormaps` list to specify a value. e.g. `colormaps$density`
- nshades: Number of colors to generate. NOTE each palette has a certain mininum required number and if you specify a value below it, the function will throw an error.
- format: one of 'hex', 'rgb', 'rgbaString'
- alpha: Either a single value between 0 and 1 or a vector of 2 elements specifying a range.

## Example

```{r eg1}
library(colormap)

colormap() # Defaults to 72 colors from the 'jet' palette.

colormap(colormap=colormaps$temperature, nshades=20) # Diff Palette

colormap(format='rgb',nshades=10) # As rgb

colormap(format='rgb',nshades=10,alpha=0.5) # Constant alpha

colormap(format='rgb',nshades=10,alpha=c(0.2,08)) # Alpha Range

colormap(format='rgbaString',nshades=10) # As rgba string
```

Finally all palettes

```{r plot, fig.height=18}
par(mfrow=c(44,1))
par(mar=rep(0.25,4))
purrr::walk(colormaps, function(x) { 
  barplot(rep(1,72), yaxt="n", space=c(0,0),border=NA,
          col=colormap(colormap=x), main = sprintf("\n\n%s",x))
  })
```

## WARNING

I have noticed that certain palettes don't generate unique colors. From my observation certain palettes can have up to one or two dupes. I have raised a [BUG](https://github.com/bpostlethwaite/colormap/issues/9) upstream, and will fix this package when that gets fixed. In the mean time you can use `unique`.

```{r dupes}
# This has no dupes
greys <- colormap(colormap = colormaps$greys)
length(greys)
length(unique(greys))

# This has dupes
thermal <- colormap(colormap = colormaps$temperature)
length(thermal)
length(unique(thermal))