---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Color Palettes from Node.js Colormap module.

This is an R package that allows you to generate colors from color palettes defined in Node [colormap](https://github.com/bpostlethwaite/colormap) module. In addition it provides scales functions for use in ggplot2 plots. In total it provides 44 distinct palettes made from sequential and/or diverging colors.

## Credits

- The [colormap](https://github.com/bpostlethwaite/colormap) Node.js module which does all the heavylifting.
- The [V8](https://github.com/jeroenooms/V8) package which allows R code to call Javascript code.
- [Bob Rudis](https://twitter.com/hrbrmstr)'s [zoneparser](https://github.com/hrbrmstr/zoneparser) package which I used as a skeleton for this pacakge.
- [Simon Garnier](https://twitter.com/sjmgarnier)'s [viridis](https://github.com/sjmgarnier/viridis) package for ggplot2 scale functions.

## Updates

[![Travis-CI Build Status](https://travis-ci.org/bhaskarvk/colormap.svg?branch=master)](https://travis-ci.org/bhaskarvk/colormap)

- 2016-08-30 Input Validation and ggplot2 scales.
- 2016-08-29 First Release.


## Installation

Requires [V8](https://cran.r-project.org/web/packages/V8/index.html)

```{r install, eval=FALSE}
if(!require("V8")) install.packages("V8")
if(!require("devtools")) install.packages("devtools")
devtools::install_github("bhaskarvk/colormap")
```

## Usage

The main function is `colormap` which takes 5 optional arguments

- colormap: A string representing one of the 44 built-in colormaps.\n You can use the `colormaps` list to specify a value. e.g. `colormaps$density`
- nshades: Number of colors to generate.
- format: one of 'hex', 'rgb', 'rgbaString'
- alpha: Between 0 & 1 to specify the transparency.
- reverse: Boolean. Whether to reverse the order of the colors returned or not.

## Example

```{r eg1}
library(colormap)

colormap() # Defaults to 72 colors from the 'jet' palette.

colormap(colormap=colormaps$temperature, nshades=20) # Diff Palette

colormap(format='rgb',nshades=10) # As rgb

colormap(format='rgb',nshades=10,alpha=0.5) # Constant alpha

colormap(format='rgbaString',nshades=10) # As rgba string
```

You also get `scale_fill_colormap` and `scale_color_colormap` functions for using these palettes in ggplot2 plots. Check `?colormap::scale_fill_colormap` for details.


```{r ggplot2}
library(ggplot2)

# Continuous color scale
ggplot(mtcars,aes(x=wt,y=mpg)) + geom_point(aes(color=hp)) +
  theme_minimal() +
  scale_color_colormap('Horse Power',
                       discrete = F,colormap = colormaps$viridis, reverse = T)

ggplot(mtcars,aes(x=wt,y=mpg)) + geom_point(aes(color=as.factor(cyl))) +
  theme_minimal() +
  scale_color_colormap('Cylinder',
                       discrete = T,colormap = colormaps$warm, reverse = T)

```

Here are two choroplethes using `scale_fill_colormap`.

```{r maps}
library(maptools)
library(scales)
library(ggplot2)
library(ggalt)
library(albersusa)
library(ggthemes)
library(colormap)

us <- usa_composite()
us_map <- fortify(us, region="name")

gg_usa <- ggplot()
gg_usa <- gg_usa + geom_map(data=us_map, map=us_map,
                    aes(x=long, y=lat, map_id=id),
                    color="#2b2b2b", size=0.1, fill=NA)
gg_usa <- gg_usa + theme_map()
gg_usa <- gg_usa + 
  geom_map(data=us@data, map=us_map,
           aes(fill=pop_2014, map_id=name),
           color="white", size=0.1) +
  coord_proj(us_laea_proj) +
  theme(legend.position="right")

gg_usa +
  scale_fill_colormap("State Population\n(2014 Estimates)", labels=comma,
                      colormap = colormaps$copper, reverse = T, discrete = F)


counties <- counties_composite()

counties_map <- fortify(counties, region="fips")

gg_counties <- ggplot()
gg_counties <- gg_counties + geom_map(data=counties_map, map=counties_map,
                    aes(x=long, y=lat, map_id=id),
                    color="#2b2b2b", size=0.1, fill=NA)
gg_counties <- gg_counties + theme_map() +
  coord_proj(us_laea_proj) +
  theme(legend.position="right")
gg_counties <- gg_counties + 
  geom_map(data=counties@data, map=counties_map,
           aes(fill=population/census_area, map_id=fips),
           color="white", size=0.1)
gg_counties +
  scale_fill_colormap("County Population Density", labels=comma, trans = 'log10',
                      colormap = colormaps$cubehelix, reverse = T, discrete = F)

```

Here is a plot showing all possible palettes.

```{r plot, fig.height=18}
par(mfrow=c(44,1))
par(mar=rep(0.25,4))
purrr::walk(colormaps, function(x) { 
  barplot(rep(1,72), yaxt="n", space=c(0,0),border=NA,
          col=colormap(colormap=x), main = sprintf("\n\n%s",x))
  })
```
